Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex
typo fix
tikz samples for data parallelism & shuffle

\TODO{Is the following paragraph best suited here? It describes an
  assumption that we make about commands, to guarantee the validity of
  our transformations. The assumption is needed due to the limitation
  of the programming model of one input one output per command.}pldi

@@

>>>>

\TODO{Is the following paragraph best suited here? It describes an
  assumption that we make about commands, to guarantee the validity of
  our transformations. The assumption is needed due to the limitation
  of the programming model of one input one output per command.}

@@

\begin{figure*}
\centering
\begin{tikzpicture}[->, >=to, auto, node distance=1cm, semithick, transform shape, inner sep=2pt]
%
\small
%
\node (M1) {};
\node (M2) [draw, right of=M1, node distance=2cm] {Map};
\node (M3) [draw, right of=M2, node distance=3cm] {GroupBy(Reduce)};
\node (M4) [right of=M3, node distance=3cm] {};
%
\path (M1) edge node {input} (M2);
\path (M2) edge node {stream} (M3);
\path (M3) edge node {output} (M4);
\end{tikzpicture}
\end{figure*}

\begin{figure*}
\newcommand{\Split}{\text{Split}}
\newcommand{\Merge}{\text{Merge}}
\newcommand{\Map}{\text{Map}}
\newcommand{\GroupBy}{\text{GroupBy}}
\newcommand{\Reduce}{\text{Reduce}}
\centering
\begin{tikzpicture}[->, >=to, auto, node distance=0.6cm, semithick, transform shape, inner sep=1.75pt]
%
\footnotesize
%
\node (M1) {};
\node (M2) [draw, right of=M1, node distance=1.3cm] {$\Split$};
\node (M3) [right of=M2, node distance=1.5cm] {};
\node (M4) [right of=M3, node distance=2.5cm] {};
\node (M5) [draw, right of=M4, node distance=2.2cm] {$\Merge$};
\node (M6) [draw, right of=M5, node distance=3.8cm] {$\GroupBy(K_2,\Reduce)$};
\node (M7) [draw, right of=M6, node distance=3cm] {$\Merge_K$};
\node (M8) [right of=M7, node distance=2cm] {};
%
\node (T3) [draw, above of=M3] {$\Map$};
\node (T4) [draw, above of=M4] {$\Split_K$};
\node (T5) [draw, above of=M5] {$\Merge$};
\node (T6) [draw, above of=M6] {$\GroupBy(K_1,\Reduce)$};
%
\node (B3) [draw, below of=M3] {$\Map$};
\node (B4) [draw, below of=M4] {$\Split_K$};
\node (B5) [draw, below of=M5] {$\Merge$};
\node (B6) [draw, below of=M6] {$\GroupBy(K_3,\Reduce)$};
%
\path (M1) edge node {$A$} (M2);
\path (M2) edge[bend left=10] node {$A$} (T3);
\path (M2) edge[bend right=10] node[swap] {$A$} (B3);
\path (M5) edge node {$K_2 \times B$} (M6);
\path (M6) edge (M7);
\path (M7) edge node {$K \times B$} (M8);
%
\path (T3) edge node {$K \times B$} (T4);
\path (T4) edge (T5);
\path (T4) edge (M5);
\path (T4.330) edge[bend right=10] (B5.170);
\path (T5) edge node {$K_1 \times B$} (T6);
\path (T6) edge[bend left=10] node {$K_1 \times B$} (M7);
%
\path (B3) edge node {$K \times B$} (B4);
\path (B4) edge (B5);
\path (B4) edge (M5);
\path (B4.30) edge[bend left=10] (T5.190);
\path (B5) edge node {$K_3 \times B$} (B6);
\path (B6) edge[bend right=10] node[swap] {$K_3 \times B$} (M7);
%
\end{tikzpicture}
\caption{Distributed implementation of the map-reduce pipeline $\Map \gg \GroupBy(K,\Reduce)$.}
\label{fig:mapReduce}
\end{figure*}
